A Switching Planner for Combined Task and Observation Planning

### 2011-02-04 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
shrinking and growing, all at the same time.  Not sure how we are going to get this down to 6 pages yet.
completed introduction

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit useful
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We evaluate our approach
in large problems from a realistic robot exploration domain.

@@

\section{Propositional Decision-Theoretic Planning}
\input{prop-dtp.tex}

@@

\section{Related Work}
\input{relatex.tex}

>>>>

From an automated planning perspective the problem of practical mobile
robot control in realistic environments poses many important and
contrary challenges.  On the one hand, the planning process must be
lightweight, robust, and timely. Over the lifetime of the robot it
must always respond quickly with new plans that accommodate exogenous
events, changing objectives, and the underlying unpredictability of
the environment.  On the other hand, in order to exhibit efficient
behaviours the planning process must perform computationally expensive
reasoning about contingencies and possible revisions of subjective
beliefs according to quantitatively modelled uncertainty in acting and
sensing.
%%
Towards addressing these challenges, we develop a \emph{continual
planning} approach that {\em switches} between using a fast
satisficing ``classical'' planner, to decide on the overall strategy,
and decision-theoretic planning to solve small subproblems where
deeper consideration of the sensing model is both practical, and can
significantly impact overall performance. We evaluate our approach
in large problems from a realistic robot exploration domain.

@@

%% \section{Propositional Decision-Theoretic Planning}
%% \input{prop-dtp.tex}

\section{Background and Related Work}
\input{relatex.tex}

@@
